---
title: "shinyBN"
author: "Jiajin Chen,Yongyue Wei"
date: "2018年5月14日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
shinyBN is a web application for construct, display and inference with Bayesian Network interactively.

## Get Start:
To install shinyBN from CRAN:
```
install.packages("shinyBN")
```

To install shinyBN from Github for the latest developmental version:
```
devtools::install_github('JiajinChen/shnyBN')
```

To launch the app:
```
shinyBN:run_shinyBN()
```

## Example
### Main Page
![](http://image.baidu.com/search/detail?ct=503316480&z=0&ipn=d&word=%E5%9B%BE%E7%89%87&hs=0&pn=9&spn=0&di=154169740560&pi=0&rn=1&tn=baiduimagedetail&is=0%2C0&ie=utf-8&oe=utf-8&cl=2&lm=-1&cs=415293130%2C2419074865&os=1556766946%2C250663840&simid=4145280632%2C499508967&adpicid=0&lpn=0&ln=30&fr=ala&fm=&sme=&cg=&bdtype=0&oriquery=&objurl=http%3A%2F%2Fimg.zcool.cn%2Fcommunity%2F0117e2571b8b246ac72538120dd8a4.jpg%401280w_1l_2o_100sh.jpg&fromurl=ippr_z2C%24qAzdH3FAzdH3Fooo_z%26e3Bzv55s_z%26e3Bv54_z%26e3BvgAzdH3Fo56hAzdH3FZMTYoNTMzMDQ%3D_z%26e3Bip4s&gsm=0&islist=&querylist=)

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
